# Aktionen pro Visit/Fingerprint

## Setup


```{r load-libs}
library(tidyverse)
library(lubridate)
library(gt)
library(targets)
library(ggpubr)
library(scales)
library(ggfittext)
library(easystats)
library(ggokabeito)
```

```{r source-common-start}
source("_common.r")
```



```{r load-targets}
tar_load(c(
  course_and_uni_per_visit,
  n_action,
  n_action_type,
  n_action_w_date,
  time_visit_wday,
  time_visit_wday_fingerprint,
  data_separated_filtered_date_uni_course,
  n_action_fingerprint
))
```


## Aktionen pro idvisit/fingerprint - Mit den 499er-Daten


```{r n_action_lt_500}
n_action_lt_500 <-
  n_action |>
  filter(nr_max != 499)

n_action_lt_500 |>
  describe_distribution(nr_max) |>
  gt() |>
  fmt_number(columns = where(is.numeric), decimals = 2)
```


```{r n_action_lt_500_fingerprint_unique}
n_action_lt_500_fingerprint_unique <-
  n_action_fingerprint |>
  filter(nr_max != 499) |>
  distinct(fingerprint, .keep_all = TRUE)

n_action_lt_500_fingerprint_unique |>
  describe_distribution(nr_max) |>
  gt() |>
  fmt_number(columns = where(is.numeric), decimals = 2)
```


### idvisit


```{r plot-count-action}
#| error: true
n_action_avg = mean(n_action$nr_max) |> round(0)
n_action_median = median(n_action$nr_max) |> round(0)
n_action_sd = sd(n_action$nr_max) |> round(0)
n_action_iqr = IQR(n_action$nr_max) |> round(0)

n_action |>
  ggplot() +
  geom_histogram(aes(x = nr_max)) +
  labs(
    x = "Anzahl von Aktionen pro Visit",
    y = "n",
    caption = "Der vertikale Strich zeigt den Mittelwert; der horizontale MW±SD"
  ) +
  theme_minimal() +
  geom_vline(xintercept = n_action_avg, color = palette_okabe_ito()[1]) +
  geom_segment(
    x = n_action_avg - n_action_sd,
    y = 0,
    xend = n_action_avg + n_action_sd,
    yend = 0,
    color = palette_okabe_ito()[2],
    size = 2
  ) +
  annotate(
    "label",
    x = n_action_avg,
    y = 1500,
    label = paste0("MW = ", n_action_avg)
  ) +
  annotate(
    "label",
    x = n_action_avg + n_action_sd,
    y = 0,
    label = paste0("SD = ", n_action_sd)
  )
#geom_label(aes(x = n_action_avg), y = 1, label = "Mean")

n_action |>
  ggplot() +
  geom_histogram(aes(x = nr_max)) +
  labs(
    x = "Anzahl von Aktionen pro Visit",
    y = "n",
    caption = "Der vertikale Strich zeigt den Median; der horizontale Median±IQR"
  ) +
  theme_minimal() +
  geom_vline(xintercept = n_action_median, color = palette_okabe_ito()[1]) +
  geom_segment(
    x = n_action_median - n_action_iqr,
    y = 0,
    xend = n_action_median + n_action_iqr,
    yend = 0,
    color = palette_okabe_ito()[2],
    size = 2
  ) +
  annotate(
    "label",
    x = n_action_median,
    y = 1500,
    label = paste0("Md = ", n_action_median)
  ) +
  annotate(
    "label",
    x = n_action_median + n_action_iqr,
    y = 0,
    label = paste0("IQR = ", n_action_iqr)
  )
#geom_label(aes(x = n_action_avg), y = 1, label = "Mean")
```



- Mittelwert der Aktionen pro Visit: `r round(n_action_avg, 2)`.
- SD der Aktionen pro Visit: `r round(n_action_sd, 2)`.
- MD:  `r round(n_action_median, 2)`.
- IQR: : `r round(n_action_iqr, 2)`. 

### fingerprint


```{r plot-count-action-fingerprint}
#| error: true
n_action_fingerprint_avg = mean(n_action_fingerprint$nr_max) |> round(0)
n_action_fingerprint_median = median(n_action_fingerprint$nr_max) |> round(0)
n_action_fingerprint_sd = sd(n_action_fingerprint$nr_max) |> round(0)
n_action_fingerprint_iqr = IQR(n_action_fingerprint$nr_max) |> round(0)

n_action_fingerprint |>
  ggplot() +
  geom_histogram(aes(x = nr_max)) +
  labs(
    x = "Anzahl von Aktionen pro Visit",
    y = "n",
    caption = "Der vertikale Strich zeigt den Mittelwert; der horizontale MW±SD"
  ) +
  theme_minimal() +
  geom_vline(
    xintercept = n_action_fingerprint_avg,
    color = palette_okabe_ito()[1]
  ) +
  geom_segment(
    x = n_action_fingerprint_avg - n_action_fingerprint_sd,
    y = 0,
    xend = n_action_fingerprint_avg + n_action_fingerprint_sd,
    yend = 0,
    color = palette_okabe_ito()[2],
    size = 2
  ) +
  annotate(
    "label",
    x = n_action_fingerprint_avg,
    y = 1500,
    label = paste0("MW = ", n_action_fingerprint_avg)
  ) +
  annotate(
    "label",
    x = n_action_fingerprint_avg + n_action_fingerprint_sd,
    y = 0,
    label = paste0("SD = ", n_action_fingerprint_sd)
  )
#geom_label(aes(x = n_action_fingerprint_avg), y = 1, label = "Mean")

n_action_fingerprint |>
  ggplot() +
  geom_histogram(aes(x = nr_max)) +
  labs(
    x = "Anzahl von Aktionen pro Visit",
    y = "n",
    caption = "Der vertikale Strich zeigt den Median; der horizontale Median±IQR"
  ) +
  theme_minimal() +
  geom_vline(
    xintercept = n_action_fingerprint_median,
    color = palette_okabe_ito()[1]
  ) +
  geom_segment(
    x = n_action_fingerprint_median - n_action_fingerprint_iqr,
    y = 0,
    xend = n_action_fingerprint_median + n_action_fingerprint_iqr,
    yend = 0,
    color = palette_okabe_ito()[2],
    size = 2
  ) +
  annotate(
    "label",
    x = n_action_fingerprint_median,
    y = 1500,
    label = paste0("Md = ", n_action_fingerprint_median)
  ) +
  annotate(
    "label",
    x = n_action_fingerprint_median + n_action_fingerprint_iqr,
    y = 0,
    label = paste0("IQR = ", n_action_fingerprint_iqr)
  )
#geom_label(aes(x = n_action_fingerprint_avg), y = 1, label = "Mean")
```

## Ohne 499er-Daten

### idvisit

```{r plot-count-action-2}
n_action_avg2 = mean(n_action_lt_500$nr_max) |> round(0)
n_action_sd2 = sd(n_action_lt_500$nr_max) |> round(2)

n_action_lt_500 |>
  ggplot() +
  geom_histogram(aes(x = nr_max)) +
  labs(
    x = "Anzahl von Aktionen pro Visit",
    y = "n",
    title = "Verteilung der User-Aktionen pro Visit",
    caption = "Der vertikale Strich zeigt den Mittelwert; der horizontale die SD"
  ) +
  theme_minimal() +
  geom_vline(xintercept = n_action_avg2, color = palette_okabe_ito()[1]) +
  geom_segment(
    x = n_action_avg - n_action_sd2,
    y = 0,
    xend = n_action_avg2 + n_action_sd2,
    yend = 0,
    color = palette_okabe_ito()[2],
    size = 2
  ) +
  annotate(
    "label",
    x = n_action_avg2,
    y = 1500,
    label = paste0("MW = ", n_action_avg2)
  ) +
  annotate(
    "label",
    x = n_action_avg2 + n_action_sd2,
    y = 0,
    label = paste0("SD = ", n_action_sd2)
  )
#geom_label(aes(x = n_action_avg), y = 1, label = "Mean")
```



- Mittelwert der Aktionen pro Visit: `r round(n_action_avg2, 2)`.
- SD der Aktionen pro Visit: `r round(n_action_sd2, 2)`.

### fingerprint unique

```{r plot-count-action-2_2}
n_action_fingerprint_avg2 = mean(n_action_lt_500_fingerprint_unique$nr_max) |>
  round(0)
n_action_fingerprint_sd2 = sd(n_action_lt_500_fingerprint_unique$nr_max) |>
  round(2)

n_action_lt_500_fingerprint_unique |>
  ggplot() +
  geom_histogram(aes(x = nr_max)) +
  labs(
    x = "Anzahl von Aktionen pro Visit",
    y = "n",
    title = "Verteilung der User-Aktionen pro Visit",
    caption = "Der vertikale Strich zeigt den Mittelwert; der horizontale die SD"
  ) +
  theme_minimal() +
  geom_vline(
    xintercept = n_action_fingerprint_avg2,
    color = palette_okabe_ito()[1]
  ) +
  geom_segment(
    x = n_action_fingerprint_avg - n_action_fingerprint_sd2,
    y = 0,
    xend = n_action_fingerprint_avg2 + n_action_fingerprint_sd2,
    yend = 0,
    color = palette_okabe_ito()[2],
    size = 2
  ) +
  annotate(
    "label",
    x = n_action_fingerprint_avg2,
    y = 1500,
    label = paste0("MW = ", n_action_fingerprint_avg2)
  ) +
  annotate(
    "label",
    x = n_action_fingerprint_avg2 + n_action_fingerprint_sd2,
    y = 0,
    label = paste0("SD = ", n_action_fingerprint_sd2)
  )
#geom_label(aes(x = n_action_avg), y = 1, label = "Mean")
```




## Anzahl Aktionen im Zeitverlauf

### Monat

#### idvisit 

```{r}
n_action_w_date |>
  ggplot(aes(x = month_date, y = nr_max)) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(
    fun.data = mean_sdl,
    fun.args = list(mult = 1),
    geom = "errorbar",
    width = 0.2
  ) +
  geom_smooth(method = "lm") +
  labs(title = "The number of actions per visit has incresed over time")
```





```{r n_action_w_date-plot}
n_action_w_date |>
  ggplot(aes(x = month_date, y = nr_max)) +
  geom_jitter(alpha = .1)
```

#### fingerprint unique

```{r}
n_action_w_date_fingerprint_unique <-
  n_action_w_date_fingerprint |>
  distinct(fingerprint, .keep_all = TRUE)

n_action_w_date_fingerprint_unique |>
  ggplot(aes(x = month_date, y = nr_max)) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(
    fun.data = mean_sdl,
    fun.args = list(mult = 1),
    geom = "errorbar",
    width = 0.2
  ) +
  geom_smooth(method = "lm") +
  labs(title = "The number of actions per visit has incresed over time")
```





```{r n_action_w_date-plot_2}
n_action_w_date_fingerprint_unique |>
  ggplot(aes(x = month_date, y = nr_max)) +
  geom_jitter(alpha = .1)
```



### Regression (Monat)

#### idvisit
```{r}
lm(nr_max ~ month_date, data = n_action_w_date)
```

#### fingerprint
```{r}
lm(nr_max ~ month_date, data = n_action_w_date_fingerprint)
```


#### fingerprint unique
```{r}
lm(nr_max ~ month_date, data = n_action_w_date_fingerprint_unique)
```

### Woche
#### idvisit
```{r}
n_action_w_date |>
  mutate(week_date = as.Date(week_date)) |>
  ggplot(aes(x = week_date, y = nr_max)) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun.data = mean_sdl, geom = "errorbar", width = 0.2) +
  geom_smooth(method = "lm") +
  labs(title = "The number of actions per visit has incresed over time")
```

#### fingerprint
```{r}
n_action_w_date_fingerprint |>
  mutate(week_date = as.Date(week_date)) |>
  ggplot(aes(x = week_date, y = nr_max)) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun.data = mean_sdl, geom = "errorbar", width = 0.2) +
  geom_smooth(method = "lm") +
  labs(title = "The number of actions per fingerprint has incresed over time")
```

#### fingerprint unique
```{r}
n_action_w_date_fingerprint_unique <-
  n_action_w_date_fingerprint |>
  distinct(fingerprint, .keep_all = TRUE)

n_action_w_date_fingerprint_unique |>
  mutate(week_date = as.Date(week_date)) |>
  ggplot(aes(x = week_date, y = nr_max)) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun.data = mean_sdl, geom = "errorbar", width = 0.2) +
  geom_smooth(method = "lm") +
  labs(title = "The number of actions per fingerprint has incresed over time")
```


### Regression (Woche)


#### idvisit

```{r}
lm(nr_max ~ week_date, data = n_action_w_date)
```

#### fingerprint
```{r}
lm(nr_max ~ week_date, data = n_action_w_date_fingerprint)
```


## fingerprint unqiue
```{r}
lm(nr_max ~ week_date, data = n_action_w_date_fingerprint_unique)
```


## Gruppierung der Visits/fingerprints nach Anzahl der Aktionen


### idvisit

```{r}
n_action_lt_500 <-
  n_action_lt_500 |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  )
```

```{r}
n_action_lt_500 |>
  count(n_actions_type) |>
  gt()
```

```{r}
ggplot(n_action_lt_500) +
  aes(x = n_actions_type) +
  geom_bar()
```

#### fingerprint

```{r}
n_action_lt_500_fingerprint <-
  n_action_lt_500_fingerprint |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  )
```

```{r}
n_action_lt_500_fingerprint |>
  count(n_actions_type) |>
  gt()
```

```{r}
ggplot(n_action_lt_500_fingerprint) +
  aes(x = n_actions_type) +
  geom_bar()
```

#### fingerprint unique

```{r}
n_action_lt_500_fingerprint_unique <-
  n_action_lt_500_fingerprint_unique |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  )
```

```{r}
n_action_lt_500_fingerprint_unique |>
  count(n_actions_type) |>
  gt()
```

```{r}
ggplot(n_action_lt_500_fingerprint_unique) +
  aes(x = n_actions_type) +
  geom_bar()
```

## Gruppierung der Visits im Zeitverlauf

### idvisit

#### Absolutzahlen

```{r}
n_action_w_date |>
  group_by(month_date) |>
  count(nr_max) |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  ) |>
  count(n_actions_type) |>
  ggplot(aes(
    x = month_date,
    y = n,
    color = n_actions_type,
    group = n_actions_type
  )) +
  geom_point() +
  geom_line()
```


#### Relative Anteile

```{r}
library(data.table) # Ensure data.table is loaded if not already
library(ggplot2)
library(scales) # Needed for label_percent()

n_action_w_date |>
  group_by(month_date) |>
  count(nr_max) |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  ) |>
  # 1. Count the number of users by month and type
  count(month_date, n_actions_type) |>
  # 2. Group ONLY by month_date
  group_by(month_date) |>
  # 3. Calculate the proportion (relative frequency)
  mutate(
    proportion = n / sum(n)
  ) |>
  # 4. Create the stacked area chart
  ggplot(aes(
    x = month_date,
    y = proportion,
    fill = n_actions_type # Use 'fill' for stacking
  )) +
  # Use geom_area() with position="fill" to stack and normalize to 100%
  geom_area(position = "fill") +

  # Optional: Customize the y-axis to show percentages
  scale_y_continuous(labels = scales::label_percent()) +

  # Optional: Add clear labels
  labs(
    y = "Proportion of Users",
    fill = "User Type",
    title = "User Type Distribution Over Time"
  )
```

### fingerprint

#### Absolutzahlen
```{r}
n_action_w_date_fingerprint |>
  group_by(month_date) |>
  count(nr_max) |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  ) |>
  count(n_actions_type) |>
  ggplot(aes(
    x = month_date,
    y = n,
    color = n_actions_type,
    group = n_actions_type
  )) +
  geom_point() +
  geom_line()
```

### fingerprint unique

```{r}
n_action_w_date_fingerprint_unique |>
  group_by(month_date) |>
  count(nr_max) |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  ) |>
  count(n_actions_type) |>
  ggplot(aes(
    x = month_date,
    y = n,
    color = n_actions_type,
    group = n_actions_type
  )) +
  geom_point() +
  geom_line()
```


#### Relative Anteile

```{r}
library(data.table) # Ensure data.table is loaded if not already
library(ggplot2)
library(scales) # Needed for label_percent()

n_action_w_date_fingerprint_unique |>
  group_by(month_date) |>
  count(nr_max) |>
  mutate(
    n_actions_type = case_when(
      nr_max < 30 ~ "glimpser",
      nr_max < 300 ~ "serious user",
      TRUE ~ "heavy user"
    )
  ) |>
  # 1. Count the number of users by month and type
  count(month_date, n_actions_type) |>
  # 2. Group ONLY by month_date
  group_by(month_date) |>
  # 3. Calculate the proportion (relative frequency)
  mutate(
    proportion = n / sum(n)
  ) |>
  # 4. Create the stacked area chart
  ggplot(aes(
    x = month_date,
    y = proportion,
    fill = n_actions_type # Use 'fill' for stacking
  )) +
  # Use geom_area() with position="fill" to stack and normalize to 100%
  geom_area(position = "fill") +

  # Optional: Customize the y-axis to show percentages
  scale_y_continuous(labels = scales::label_percent()) +

  # Optional: Add clear labels
  labs(
    y = "Proportion of Users",
    fill = "User Type",
    title = "User Type Distribution Over Time"
  )
```

