
# KI-Gebrauch


## Setup


```{r load-libs}
library(tidyverse)
library(lubridate)
library(gt)
library(targets)
library(ggpubr)
library(scales)
# library(ggfittext)
library(easystats)
library(data.table)
library(tinytable)
# library(ggokabeito)
```

```{r source-common-start}
source("_common.r")
```



```{r load-targets}
tar_load(
  c(
    ai_transcript_clicks_per_month,
    data_long,
    data_separated_distinct_slice,
    data_separated_filtered,
    idvisit_has_llm,
    llm_response_text,
    n_mc_answers_selected,
    mc_answers_with_timestamps,
    prompt_length,
    prompt_length_date_uni_course,
    time_spent_w_course_university,
    llm_response_text_date_course_uni
  )
)
```



## Interaktion mit dem LLM

Berechnungsgrundlage: Für diese Analyse wurden alle Events der Kategorie `llm` gefiltert.

### Art und Anzahl der Interaktionen mit dem LLM



```{r data_separated_filtered_ai}
data_separated_filtered_ai <-
  data_separated_filtered |>
  filter(type == "eventcategory") |>
  filter(str_detect(value, "llm")) |>
  count(value, sort = TRUE) |>
  mutate(prop = n / sum(n))

data_separated_filtered_ai
```

```{r}
data_separated_filtered_ai |>
  mutate(prop = round(prop, 3)) |>
  ggtexttable()
```


## Anzahl der `message_to_llm` 



```{r llm_interactions}
llm_interactions <-
  data_separated_filtered |>
  filter(str_detect(value, "message_to_llm"))
```

### Verteilung

```{r}
llm_interactions_count <-
  llm_interactions |>
  count(idvisit, sort = TRUE) |>
  rename(messages_to_llm_n = n)

llm_interactions_count |>
  describe_distribution(messages_to_llm_n, centrality = c("mean", "median"))

```

### Diagramm

```{r}
gghistogram(
  llm_interactions_count,
  x = "messages_to_llm_n",
  bins = 10,
  add = "median"
) +
  labs(caption = "The vertical dotted line denotes the median.")
```




### Anteil Visitors, die mit dem LLM interagieren

#### idvisit
```{r data_separated_filtered_llm_interact}
data_separated_filtered_llm_interact <-
  data_separated_filtered |>
  mutate(has_llm = str_detect(value, "llm")) |>
  group_by(idvisit) |>
  summarise(llm_used_during_visit = any(has_llm == TRUE)) |>
  count(llm_used_during_visit) |>
  mutate(prop = round(n / sum(n), 2))

data_separated_filtered_llm_interact |>
  gt()
```

```{r}
data_separated_filtered_llm_interact |>
  ggtexttable()
```

#### fingerprint unique

```{r data_separated_filtered_llm_interact_fingerprint}
data_separated_filtered_llm_interact_fingerprint <-
  data_separated_filtered |>
  mutate(has_llm = str_detect(value, "llm")) |>
  group_by(fingerprint) |>
  summarise(llm_used_during_visit = any(has_llm == TRUE)) |>
  count(llm_used_during_visit) |>
  mutate(prop = round(n / sum(n), 2))

data_separated_filtered_llm_interact_fingerprint |>
  gt()
```

```{r}
data_separated_filtered_llm_interact_fingerprint |>
  ggtexttable()
```

### ... Im Zeitverlauf


#### Absolutzahlen

```{r idvisit_has_llm}
idvisit_has_llm |>
  head(30)
```


```{r idvisit_has_llm_timeline}
idvisit_has_llm_timeline <-
  idvisit_has_llm |>
  count(year_month, uses_llm) |>
  ungroup() |>
  group_by(year_month) |>
  mutate(prop = round(n / sum(n), 2))

idvisit_has_llm_timeline
```

```{r}
idvisit_has_llm_timeline |>
  ggtexttable()
```


```{r idvisit_has_llm_plot}
idvisit_has_llm |>
  count(year_month, uses_llm) |>
  ungroup() |>
  mutate(year_month_date = ymd(paste0(year_month, "-01"))) |>
  group_by(year_month_date) |>
  mutate(prop = n / sum(n)) |>
  ggplot(aes(
    x = year_month_date,
    y = prop,
    color = uses_llm,
    groups = uses_llm
  )) +
  geom_point() +
  geom_line(aes(group = uses_llm)) +
  labs(
    title = "Visitors, die mit dem LLM interagieren im Zeitverlauf (Anteile)"
  ) +
  scale_x_date(breaks = pretty_breaks())
```


```{r}
idvisit_has_llm |>
  count(year_month, uses_llm) |>
  ungroup() |>
  mutate(year_month_date = ymd(paste0(year_month, "-01"))) |>
  group_by(year_month) |>
  ggplot(aes(x = year_month_date, y = n, color = uses_llm, groups = uses_llm)) +
  geom_point() +
  geom_line(aes(group = uses_llm)) +
  labs(
    title = "Visitors, die mit dem LLM interagieren im Zeitverlauf (Anzahl)"
  ) +
  scale_x_date(breaks = pretty_breaks())
```

#### Anteile
```{r}
idvisit_has_llm |>
  count(year_month, uses_llm) |>
  ungroup() |>
  mutate(year_month_date = ymd(paste0(year_month, "-01"))) |>
  group_by(year_month_date) |>
  # ADDED: Calculate the proportion
  mutate(proportion = n / sum(n)) |>

  # Plot using the new 'proportion' variable
  ggplot(aes(x = year_month_date, y = proportion, fill = uses_llm)) +

  # ADDED: Use position = "fill"
  geom_area(position = "fill") +

  # ADDED: Format y-axis as percentage
  scale_y_continuous(labels = scales::label_percent()) +

  labs(
    title = "Anteil der Besucher, die mit dem LLM interagieren (Prozent)",
    y = "Prozentualer Anteil der Besucher",
    fill = "Interagiert mit LLM"
  ) +
  scale_x_date(breaks = pretty_breaks())
```




## Länge der Prompts (Input an das LLM)

### Überblick
```{r}
prompt_length_no_prompts <-
  prompt_length |>
  select(-any_of(c("prompt", "value", "type")))
```


```{r}
prompt_length_no_prompts |>
  describe_distribution(token_length) |>
  print_md()
```

```{r prompt_length_no_prompts-plot}
prompt_length_no_prompts |>
  ggplot(aes(x = token_length)) +
  geom_histogram(binwidth = 10) +
  labs(
    title = "Length of prompts sent to the LLM",
    x = "Prompt length (in tokens)",
    y = "Number of prompts"
  ) +
  theme_minimal()
```


```{r}
describe_distribution(
  prompt_length$prompt_length,
  centrality = c("mean", "median")
)
```



### Token-Länge nach Universitäten

```{r}
prompt_length_date_uni_course |>
  group_by(university) |>
  describe_distribution(token_length)
```

```{r prompt_length_date_uni_course-ggviolin}
ggviolin(
  prompt_length_date_uni_course,
  x = "university",
  y = "token_length",
  add = "mean_se",
) +
  theme_minimal() +
  labs(
    title = "Prompt length by university",
    x = "University",
    y = "Prompt length (in tokens)",
    caption = "The dots represent the mean and the error bars the standard error of the mean."
  ) +
  coord_flip()
```



### Token-Länge nach Kursen


```{r}
prompt_length_date_uni_course |>
  group_by(course) |>
  describe_distribution(token_length) |> 
  print_md()
```

```{r prompt_length_date_uni_course-ggviolin-per-course}
ggviolin(
  prompt_length_date_uni_course,
  x = "course",
  y = "token_length",
  add = "mean_se",
) +
  theme_minimal() +
  labs(
    title = "Prompt length by course",
    x = "University",
    y = "Prompt length (in tokens)",
    caption = "The dots represent the mean and the error bars the standard error of the mean."
  ) +
  coord_flip()
```





## Anzahl der Interaktionen bei den Usern, die mit dem LLM interagieren

### Insgesamt

```{r d_n_interactions_w_llm}
d_n_interactions_w_llm <-
  data_separated_filtered |>
  filter(type == "eventcategory") |>
  filter(str_detect(value, "llm")) |>
  group_by(idvisit) |>
  summarise(n_interactions_w_llm = n())
```

```{r d_n_interactions_w_llm-describe-distro}
d_n_interactions_w_llm |>
  select(n_interactions_w_llm) |>
  describe_distribution() |>
  print_md()
```


```{r d_n_interactions_w_llm-plot2}
d_n_interactions_w_llm |>
  ggplot(aes(x = n_interactions_w_llm)) +
  geom_histogram()
```




### Interaktionen mit dem LLM - pro Kurs und pro Uni


```{r d_n_interactions_w_llm_course}
d_n_interactions_w_llm_course <-
  data_separated_filtered |>
  filter(type == "eventcategory") |>
  filter(str_detect(value, "llm")) |>
  group_by(idvisit) |>
  slice_head(n = 1)

d_n_interactions_w_llm_course_date_course_uni <-
  d_n_interactions_w_llm_course |>
  left_join(
    time_spent_w_course_university |> mutate(idvisit = as.integer(idvisit)),
    by = "idvisit"
  )
```

```{r d_n_interactions_w_llm-describe-distro2}
d_n_interactions_w_llm_course_date_course_uni |>
  # select(n_interactions_w_llm) |>
  group_by(university, course) |>
  summarise(n = n())
```


```{r d_n_interactions_w_llm-plot}
d_n_interactions_w_llm_course_date_course_uni |>
  # select(n_interactions_w_llm) |>
  group_by(university, course) |>
  summarise(n = n()) |>
  ggplot(aes(x = reorder(course, n), y = n)) +
  geom_col() +
  coord_flip()
#facet_wrap(~ university, scales = "free_y")
```

### Interaktionen mit dem LLM - im Zeitverlauf

```{r d_n_interactions_w_llm_course_date_course_uni-plot}
d_n_interactions_w_llm_course_date_course_uni |>
  group_by(floor_date_month) |>
  summarise(n = n()) |>
  ggplot(aes(x = floor_date_month, y = n)) +
  geom_line()
#todo

```

```{r d_n_interactions_w_llm_course_date_course_uni-plot_with_semesters_shaded}
library(dplyr)
library(lubridate)
library(ggplot2)
library(tibble) # Needed for the tibble function

# --- 1. Prepare Data ---
# Your original data processing for the plot
plot_data <- d_n_interactions_w_llm_course_date_course_uni |>
  group_by(floor_date_month) |>
  summarise(n = n()) |>
  ungroup() # Ungroup after summarise for easier use with ggplot

# --- 2. Determine Plot Range for Rectangles ---
# Find the min/max year and n-count from your *processed* plot_data
min_date <- min(plot_data$floor_date_month, na.rm = TRUE)
max_date <- max(plot_data$floor_date_month, na.rm = TRUE)
min_year <- year(min_date)
max_year <- year(max_date)

# Determine the Y-axis bounds for the rectangles
y_min <- min(plot_data$n, na.rm = TRUE)
y_max <- max(plot_data$n, na.rm = TRUE)

# --- 3. Calculate the Rectangle Coordinates (rect_data) ---

# Generate years for the rectangles, ensuring we cover the full range
# including potentially starting a "winter" semester in the min_year-1
# and ending in max_year+1
rect_years <- seq(min_year - 1, max_year + 1)

# Summer semester: March 1 (Y) to July 1 (Y)
summer_rects <- tibble(year = rect_years) |>
  mutate(
    xmin = ymd(paste0(year, "-03-01")),
    xmax = ymd(paste0(year, "-07-01"))
  )

# Winter semester: October 1 (Y) to February 1 (Y+1)
winter_rects <- tibble(year = rect_years) |>
  mutate(
    xmin = ymd(paste0(year, "-10-01")),
    xmax = ymd(paste0(year + 1, "-02-01"))
  )

# Combine, set Y bounds, and filter to the actual plot area
rect_data <- bind_rows(summer_rects, winter_rects) |>
  mutate(ymin = y_min, ymax = y_max) |>
  # Only keep rectangles that are fully or partially within the plot's X range
  filter(
    xmin <= max_date,
    xmax >= min_date
  )

# --- 4. Generate the Final Plot ---
plot_data |>
  ggplot(aes(x = floor_date_month, y = n)) +
  # Add the transparent grey rectangles first
  geom_rect(
    data = rect_data,
    aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
    fill = "grey",
    alpha = 0.2,
    inherit.aes = FALSE # Essential to use the rect_data columns
  ) +
  # Then plot the lines and points on top
  geom_line() +
  geom_point() + # Added point layer for clarity at each month
  theme_minimal() +
  labs(
    title = "Number of Interactions with LLM per Course Date per University",
    x = "Month",
    y = "Number of Interactions"
  )
```

## Klick auf ein Wort im Transkript

Ausgewertet wird im Folgenden die Variable "click_transcript_word".

### Insgesamt


```{r ai-click-transcript-word}
data_separated_filtered |>
  filter(type == "subtitle") |>
  # rm empty rows:
  filter(!is.na(value) & value != "") |>
  count(click_transcript_word = str_detect(value, "click_transcript_word")) |>
  mutate(prop = round(n / sum(n), 2)) |>
  gt()
```



### Im Zeitverlauf

#### idvisit

```{r click_transcript_word_per_month}
click_transcript_word_per_month <-
  data_separated_filtered |>
  # rm all groups WITHOUT "click_transcript_word":
  group_by(idvisit) |>
  filter(!any(value = str_detect(value, "click_transcript_word"))) |>
  ungroup() |>
  mutate(date_visit = ymd_hms(value)) |>
  mutate(month_visit = floor_date(date_visit, unit = "month")) |>
  drop_na(date_visit) |>
  group_by(idvisit) |>
  slice(1) |>
  ungroup() |>
  count(month_visit)

click_transcript_word_per_month
```


```{r click_transcript_word_per_month_plot}
click_transcript_word_per_month |>
  ggplot(aes(x = month_visit, y = n)) +
  geom_line()
```

#### fingerprint unique


```{r click_transcript_word_per_month_2}
click_transcript_word_per_month_fingerprint <-
  data_separated_filtered |>
  # rm all groups WITHOUT "click_transcript_word":
  group_by(fingerprint) |>
  filter(!any(value = str_detect(value, "click_transcript_word"))) |>
  ungroup() |>
  mutate(date_visit = ymd_hms(value)) |>
  mutate(month_visit = floor_date(date_visit, unit = "month")) |>
  drop_na(date_visit) |>
  group_by(fingerprint) |>
  slice(1) |>
  ungroup() |>
  count(month_visit)

click_transcript_word_per_month_fingerprint
```


```{r click_transcript_word_per_month_plot_2}
click_transcript_word_per_month_fingerprint |>
  ggplot(aes(x = month_visit, y = n)) +
  geom_line()
```

## KI-Aktionen

### Insgesamt (ganzer Zeitraum)


```{r}
data_long |>
  head(300)
```


### Im Detail



```{r ai-actions-count}
regex_pattern <- "Category: \"(.*?)(?=', Action)"

# Explaining this regex_pattern:
# Find the literal string
# 1. `Category: ` (surrounded by quotation marks)
# 2. Capture any characters (.*?) that follow, non-greedily, until...
# 3. ...it encounters the literal sequence,  ` Action`) immediately after the captured string.

ai_actions_count <-
  data_long |>
  # slice(1:1000) |>
  filter(str_detect(value, "transcript")) |>
  mutate(category = str_extract(value, regex_pattern)) |>
  select(category) |>
  mutate(category = str_replace_all(category, "[\"']", "")) |>
  count(category, sort = TRUE)

ai_actions_count |>
  tt()
```









### KI-Klicks pro Monat

Im Objekt wird gezählt, wie oft der String `"click_transcript_word"` in den Daten (Langformat) gefunden wird, s. Target `ai_transcript_clicks_per_month` in der Targets-Pipeline.



```{r ai_transcript_clicks_per_month}
ai_transcript_clicks_per_month |>
  head(30)
```



```{r ai-click-transcript-word-months}
ai_transcript_clicks_per_month_count <-
  ai_transcript_clicks_per_month |>
  count(year_month, clicks_transcript_any) |>
  ungroup() |>
  group_by(year_month) |>
  mutate(prop = round(n / sum(n), 2))

ai_transcript_clicks_per_month_count
```


```{r}
ai_transcript_clicks_per_month_count |>
  ggtexttable()
```


```{r ai_transcript_clicks_per_month_count-plot}
ai_transcript_clicks_per_month_count |>
  mutate(date = ymd(paste0(year_month, "-01"))) |>
  ggplot(aes(x = date, y = n)) +
  geom_line(group = 1) +
  geom_point() +
  theme_minimal() +
  labs(title = "Number of AI transcript clicks per month", x = "date [months]")
```

```{r ai_transcript_clicks_per_month_count-plot_with_semesters}
# --- 1. Prepare Data and Determine Year Range ---
# We assign the processed data to a temporary variable to calculate the year range.
ai_clicks_data <- ai_transcript_clicks_per_month_count |>
  mutate(date = ymd(paste0(year_month, "-01")))

# --- 2. Calculate the Vertical Line Intercept Dates ---
# Find the min/max year in the data
min_year <- min(year(ai_clicks_data$date), na.rm = TRUE)
max_year <- max(year(ai_clicks_data$date), na.rm = TRUE)
years <- seq(min_year, max_year)

# Define the target months: February (2), March (3), July (7), October (10)
vline_dates <- expand.grid(
  year = years,
  month = c(2, 3, 7, 10)
) |>
  mutate(
    date_str = paste0(year, "-", month, "-01"),
    vline_date = ymd(date_str)
  ) |>
  # Filter to only include dates within the actual data range for plotting
  filter(
    vline_date >= min(ai_clicks_data$date) &
      vline_date <= max(ai_clicks_data$date)
  ) |>
  pull(vline_date) |>
  as.Date()

# --- 3. Generate the Final Plot ---
ai_clicks_data |>
  ggplot(aes(x = date, y = n)) +
  # Add the vertical lines
  geom_vline(
    xintercept = vline_dates,
    color = "darkred",
    linetype = "dashed",
    alpha = 0.6
  ) +
  geom_line(group = 1) +
  geom_point() +
  theme_minimal() +
  labs(title = "Number of AI transcript clicks per month", x = "date [months]")
```

```{r ai_transcript_clicks_per_month_count-plot_with_semesters_shaded}

# --- 1. Prepare Data and Determine Year Range ---
# We assign the processed data to a temporary variable to calculate the year range.
ai_clicks_data <- ai_transcript_clicks_per_month_count |>
  mutate(date = ymd(paste0(year_month, "-01")))

# Find the min/max year and n-count in the data
min_year <- min(year(ai_clicks_data$date), na.rm = TRUE)
max_year <- max(year(ai_clicks_data$date), na.rm = TRUE)
years <- seq(min_year, max_year)

# Determine the Y-axis bounds for the rectangles
y_min <- min(ai_clicks_data$n, na.rm = TRUE)
y_max <- max(ai_clicks_data$n, na.rm = TRUE)

# --- 2. Calculate the Rectangle Coordinates (rect_data) ---

# Period 1: March 1 (Y) to July 1 (Y)
rect_data_mar_jul <- tibble(year = years) |>
  mutate(
    xmin = ymd(paste0(year, "-03-01")),
    xmax = ymd(paste0(year, "-07-01"))
  )

# Period 2: October 1 (Y) to February 1 (Y+1)
# We need to include max_year + 1 in the sequence to capture the end dates
rect_data_oct_feb <- tibble(year = seq(min_year, max_year)) |>
  mutate(
    xmin = ymd(paste0(year, "-10-01")),
    xmax = ymd(paste0(year + 1, "-02-01"))
  )

# Combine, set Y bounds, and filter to the actual plot area
rect_data <- bind_rows(rect_data_mar_jul, rect_data_oct_feb) |>
  mutate(ymin = y_min, ymax = y_max) |>
  # Only keep rectangles that are fully or partially within the plot's X range
  filter(
    xmin <= max(ai_clicks_data$date, na.rm = TRUE),
    xmax >= min(ai_clicks_data$date, na.rm = TRUE)
  )

# --- 3. Generate the Final Plot ---
ai_clicks_data |>
  ggplot(aes(x = date, y = n)) +
  # Add the transparent grey rectangles first
  geom_rect(
    data = rect_data,
    aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
    fill = "grey",
    alpha = 0.2,
    inherit.aes = FALSE # Essential to use the rect_data columns
  ) +
  # Then plot the lines and points on top
  geom_line(group = 1) +
  geom_point() +
  theme_minimal() +
  labs(title = "Number of AI transcript clicks per month", x = "date [months]")
```

## Output des LLMs: `llm_response` - Tokens und Tokenlänge



### Deutsch vs. Englisch


```{r llm_response_text-count}
llm_response_text |>
  count(lang) |>
  mutate(prob = n / sum(n))
```

### Anzahl der Tokens

```{r}
llm_response_text |>
  describe_distribution(select = "tokens_n") |>
  print_md()
```

### Anzahl der Token nach Universitäten

```{r}
llm_response_text_date_course_uni |>
  group_by(university) |>
  describe_distribution(select = "tokens_n")
```

```{r}
llm_response_text_date_course_uni |>
  ggviolin(
    x = "university",
    y = "tokens_n",
    add = "mean_se"
  ) +
  theme_minimal() +
  labs(
    title = "Number of tokens in LLM responses by university",
    x = "University",
    y = "Number of tokens",
    caption = "The dots represent the mean and the error bars the standard error of the mean."
  ) +
  coord_flip()
```

### Anzahl der Token nach Kursen

```{r}
llm_response_text_date_course_uni |>
  group_by(course) |>
  describe_distribution(select = "tokens_n") |>
  print_md()

```


```{r}
llm_response_text_date_course_uni |>
  ggviolin(
    x = "course",
    y = "tokens_n",
    add = "mean_se"
  ) +
  theme_minimal() +
  labs(
    title = "Number of tokens in LLM responses by course",
    x = "Course",
    y = "Number of tokens",
    caption = "The dots represent the mean and the error bars the standard error of the mean."
  ) +
  coord_flip()
```

### Anzahl vorab existierender Fragen


#### Anzahl `verify_option_wrong` und `verify_option_correct`

##### idvisit


```{r verify_option_summary_dt}
verify_option_summary <- as.data.table(data_separated_filtered)[,
  .(idvisit, value) # keep only needed columns
][
  value %chin% c("verify_option_wrong", "verify_option_correct"), # filter
  .(verify_option = .N), # summarise count
  by = idvisit
]

verify_option_summary <- as_tibble(verify_option_summary)
```



```{r verify_option_summary}
#| eval: false
verify_option_summary <-
  data_separated_filtered |>
  group_by(idvisit) |>
  filter(value == "verify_option_wrong" | value == "verify_option_correct") |>
  summarise(verify_option = n())
```

```{r}
verify_option_summary |>
  gghistogram(x = "verify_option")
```

```{r}
verify_option_summary |>
  describe_distribution(verify_option) |>
  print_md()
```

##### fingerprint unique

```{r verify_option_summary_2}
# verify_option_summary_fingerprint <-
#   data_separated_filtered |>
#   group_by(fingerprint) |>
#   filter(value == "verify_option_wrong" | value == "verify_option_correct") |>
#   summarise(verify_option = n())

setDT(data_separated_filtered) # Ensure your data frame is a data.table

verify_option_summary_fingerprint <- data_separated_filtered[
  # 1. Filtering (i)
  value %in% c("verify_option_wrong", "verify_option_correct"),

  # 2. Summarize (.j) - calculate the count (n)
  .(verify_option = .N),

  # 3. Grouping (by)
  by = .(fingerprint)
]

verify_option_summary_fingerprint <- as_tibble(
  verify_option_summary_fingerprint
)
```

```{r}
verify_option_summary_fingerprint |>
  gghistogram(x = "verify_option")
```

```{r}
verify_option_summary_fingerprint |>
  describe_distribution(verify_option) |>
  print_md()
```

#### Anzahl `verify_option_wrong` verify_option_div_by_4 - geteilt durch 4

```{r}
verify_option_summary <-
  verify_option_summary |>
  mutate(verify_option_div_by_4 = verify_option / 4)

verify_option_summary |>
  gghistogram(x = "verify_option_div_by_4")
```

```{r}
verify_option_summary |>
  mutate(verify_option_div_by_4 = verify_option / 4) |>
  describe_distribution(verify_option_div_by_4) |>
  print_md()
```

#### Anzahl "Multiple choice answer selected"

```{r}
check_if_both_methods_give_same_number <-
  n_mc_answers_selected |>
  full_join(verify_option_summary)

check_if_both_methods_give_same_number |>
  head(20) |>
  gt()
```

Nein, beide Methoden liefern *nicht* die gleiche Zahl.


####  "Multiple choice answer selected" im Zeitverlauf

```{r mc_answers_with_timestamps}
mc_answers_with_timestamps <-
  mc_answers_with_timestamps |>
  mutate(month_start = floor_date(timestamp, "month")) |>
  ungroup() |>
  arrange(timestamp) |>
  mutate(n_cumulated = cumsum(n)) |>
  mutate(date = as.Date(timestamp))

lim <- c(
  min(mc_answers_with_timestamps$date),
  max(mc_answers_with_timestamps$date)
)

mc_answers_with_timestamps |>
  ggplot(aes(x = date, y = n_cumulated)) +
  scale_x_date(limits = lim, labels = scales::label_date_short()) +
  geom_point() +
  geom_line()
```

#### Anzahl `generate_questionaire`

```{r generate_questionaire_summary}
# generate_questionaire_summary <-
#   data_separated_filtered |>
#   group_by(idvisit) |>
#   filter(value == "generate_questionaire") |>
#   summarise(generate_questionaire = n())

setDT(data_separated_filtered) # Convert the data.frame to a data.table in place

generate_questionaire_summary <- data_separated_filtered[
  # 1. Filtering (i)
  value == "generate_questionaire",

  # 2. Summarize (.j) - calculate the count (.N) and rename it
  .(generate_questionaire = .N),

  # 3. Grouping (by)
  by = .(idvisit)
]
```


```{r}
generate_questionaire_summary |>
  describe_distribution(generate_questionaire) |>
  print_md()
```





#### Anzahl vorab existierender Fragen


```{r prior_existing_questions_summary}
setDT(generate_questionaire_summary)
setDT(verify_option_summary)

# 1. Full Join (Merge)
# Use the 'merge' function with all.x=TRUE and all.y=TRUE for a full join
# Assumes the join column is 'idvisit' as used in your previous examples
prior_existing_questions_summary <- merge(
  generate_questionaire_summary,
  verify_option_summary,
  by = "idvisit",
  all = TRUE
)

# 2. Mutate (Calculation)
# Use .j to create the new column
prior_existing_questions_summary[,
  prior_existing_questions_n := verify_option - generate_questionaire
]

# prior_existing_questions_summary <-
#   generate_questionaire_summary |>
#   full_join(verify_option_summary) |>
#   mutate(prior_existing_questions_n = verify_option - generate_questionaire)
```


```{r}
prior_existing_questions_summary |>
  # drop_na() |>
  gghistogram(x = "prior_existing_questions_n")
```


```{r}
prior_existing_questions_summary |>
  describe_distribution(prior_existing_questions_n) |>
  print_md()
```










## Input zum LLM: `message_to_llm` - Tokens und Tokenlänge

```{r}
prompt_length |>
  head()
```

```{r}
prompt_length |>
  describe_distribution(token_length)
```

```{r}
prompt_length |>
  ggplot(aes(x = token_length)) +
  geom_histogram(binwidth = 10) +
  labs(
    title = "Length of prompts sent to the LLM",
    x = "Prompt length (in tokens)",
    y = "Number of prompts"
  ) +
  theme_minimal()
```





